Enforced Invariant Confluence

### 2020-01-28 doc/the_vldb_journal_paper/changelog.tex
Minor changelog reword.

  \item (Section 4.1)
    We expanded the correctness proof of our interactive decision procedure. A
    key step in understanding the correctness of our interactive invariant
    confluence decision procedure---namely that $I$-reachable and
    $(I-NR)$-reachable states were equal---was omitted from our conference
    paper. We added a formal proof of this fact as well as a few other minor
    elaborations.

>>>>

  \item (Section 4.1)
    We expanded the correctness proof of our interactive decision procedure. A
    key step in understanding the correctness of our interactive invariant
    confluence decision procedure---namely that $I$-reachable and
    $(I-NR)$-reachable states are equal---was omitted from our conference
    paper. We added a formal proof of this fact as well as a few other minor
    elaborations.
